Event History Analysis for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2025-07-14 manuscript/manuscript.Rmd
update filename disclosures
update doi

All of the submitted manuscript and Supplemental Material was previously posted to a preprint archive: https://doi.org/10.31234/osf.io/57bh6

@@

Supplemental Material: Panis_Ramsey_suppl_material.pdf

>>>>

All of the submitted manuscript and Supplemental Material was previously posted to a preprint archive: https://doi.org/10.31234/osf.io/57bh6_v2

@@

Supplemental Material: Panis_Ramsey_suppl_material_R1.pdf

### 2025-07-14 manuscript/manuscript.tex
update filename disclosures
update doi

All of the submitted manuscript and Supplemental Material was previously posted to a preprint archive: \url{https://doi.org/10.31234/osf.io/57bh6}

@@

Supplemental Material: Panis\_Ramsey\_suppl\_material.pdf

>>>>

All of the submitted manuscript and Supplemental Material was previously posted to a preprint archive: \url{https://doi.org/10.31234/osf.io/57bh6_v2}

@@

Supplemental Material: Panis\_Ramsey\_suppl\_material\_R1.pdf
